Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-01 Manuscript/Tabs/sim_binom_var_slct_tab.tex

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.88 & 0.58 & 0.71 & 0.69 & 0.93 & 0.88 & 0.49 \\ 
   50 & Precision &  & 0.38 & 0.60 & 0.59 & 0.77 & 0.80 & 0.04 \\ 
  100 & Precision &  & 0.35 & 0.62 & 0.65 & 0.82 & 0.77 & 0.02 \\ 
  200 & Precision &  & 0.29 & 0.65 & 0.57 & 0.21 & 0.74 & 0.03 \\ 
    4 & Recall & 1.00 & 0.54 & 0.61 & 0.54 & 0.38 & 0.97 & 0.55 \\ 
   10 & Recall & 0.92 & 0.46 & 0.50 & 0.54 & 0.38 & 0.97 & 0.31 \\ 
   50 & Recall & 0.00 & 0.34 & 0.30 & 0.30 & 0.32 & 0.90 & 0.07 \\ 
  100 & Recall &  & 0.27 & 0.30 & 0.25 & 0.27 & 0.92 & 0.06 \\ 
  200 & Recall &  & 0.27 & 0.25 & 0.29 & 0.56 & 0.92 & 0.05 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.89 & 0.18 & 0.35 & 0.36 & 0.47 & 0.86 & 0.10 \\ 
   50 & MCC &  & 0.25 & 0.34 & 0.36 & 0.45 & 0.83 & -0.04 \\ 
  100 & MCC &  & 0.24 & 0.37 & 0.37 & 0.45 & 0.82 & -0.01 \\ 
  200 & MCC &  & 0.23 & 0.36 & 0.36 & 0.23 & 0.81 & 0.01 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.88 & 0.58 & 0.71 & 0.69 & 0.93 & 0.88 & 0.89 \\ 
   50 & Precision &  & 0.38 & 0.60 & 0.59 & 0.77 & 0.80 & 0.52 \\ 
  100 & Precision &  & 0.35 & 0.62 & 0.65 & 0.82 & 0.77 & 0.42 \\ 
  200 & Precision &  & 0.29 & 0.65 & 0.57 & 0.21 & 0.74 & 0.36 \\ 
    4 & Recall & 1.00 & 0.54 & 0.61 & 0.54 & 0.38 & 0.97 & 0.55 \\ 
   10 & Recall & 0.92 & 0.46 & 0.50 & 0.54 & 0.38 & 0.97 & 0.54 \\ 
   50 & Recall & 0.00 & 0.34 & 0.30 & 0.30 & 0.32 & 0.90 & 0.55 \\ 
  100 & Recall &  & 0.27 & 0.30 & 0.25 & 0.27 & 0.92 & 0.54 \\ 
  200 & Recall &  & 0.27 & 0.25 & 0.29 & 0.56 & 0.92 & 0.53 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.89 & 0.18 & 0.35 & 0.36 & 0.47 & 0.86 & 0.55 \\ 
   50 & MCC &  & 0.25 & 0.34 & 0.36 & 0.45 & 0.83 & 0.47 \\ 
  100 & MCC &  & 0.24 & 0.37 & 0.37 & 0.45 & 0.82 & 0.43 \\ 
  200 & MCC &  & 0.23 & 0.36 & 0.36 & 0.23 & 0.81 & 0.40 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

### 2022-03-01 Manuscript/Tabs/sim_lnr_binom_var_slct_tab.tex

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.94 & 0.61 & 0.97 & 0.98 & 0.55 & 0.74 & 0.69 \\ 
   50 & Precision &  & 0.35 & 0.59 & 0.68 & 0.26 & 0.59 & 0.19 \\ 
  100 & Precision &  & 0.28 & 0.47 & 0.51 & 0.30 & 0.46 & 0.15 \\ 
  200 & Precision &  & 0.26 & 0.44 & 0.42 & 0.38 & 0.41 & 0.10 \\ 
    4 & Recall & 1.00 & 1.00 & 0.85 & 0.78 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 1.00 & 0.96 & 0.97 & 0.99 & 1.00 & 0.77 \\ 
   50 & Recall & 0.00 & 1.00 & 0.88 & 0.74 & 0.92 & 1.00 & 0.33 \\ 
  100 & Recall &  & 1.00 & 0.78 & 0.56 & 0.89 & 1.00 & 0.27 \\ 
  200 & Recall &  & 1.00 & 0.67 & 0.48 & 0.89 & 0.99 & 0.28 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.94 & 0.58 & 0.95 & 0.96 & 0.49 & 0.72 & 0.52 \\ 
   50 & MCC &  & 0.52 & 0.66 & 0.65 & 0.37 & 0.73 & 0.15 \\ 
  100 & MCC &  & 0.49 & 0.55 & 0.47 & 0.43 & 0.65 & 0.15 \\ 
  200 & MCC &  & 0.49 & 0.49 & 0.39 & 0.47 & 0.62 & 0.13 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.94 & 0.61 & 0.97 & 0.98 & 0.55 & 0.74 & 0.91 \\ 
   50 & Precision &  & 0.35 & 0.59 & 0.68 & 0.26 & 0.59 & 0.61 \\ 
  100 & Precision &  & 0.28 & 0.47 & 0.51 & 0.30 & 0.46 & 0.57 \\ 
  200 & Precision &  & 0.26 & 0.44 & 0.42 & 0.38 & 0.41 & 0.38 \\ 
    4 & Recall & 1.00 & 1.00 & 0.85 & 0.78 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 1.00 & 0.96 & 0.97 & 0.99 & 1.00 & 1.00 \\ 
   50 & Recall & 0.00 & 1.00 & 0.88 & 0.74 & 0.92 & 1.00 & 1.00 \\ 
  100 & Recall &  & 1.00 & 0.78 & 0.56 & 0.89 & 1.00 & 0.99 \\ 
  200 & Recall &  & 1.00 & 0.67 & 0.48 & 0.89 & 0.99 & 0.98 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.94 & 0.58 & 0.95 & 0.96 & 0.49 & 0.72 & 0.91 \\ 
   50 & MCC &  & 0.52 & 0.66 & 0.65 & 0.37 & 0.73 & 0.74 \\ 
  100 & MCC &  & 0.49 & 0.55 & 0.47 & 0.43 & 0.65 & 0.72 \\ 
  200 & MCC &  & 0.49 & 0.49 & 0.39 & 0.47 & 0.62 & 0.58 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

### 2022-03-01 Manuscript/Tabs/sim_lnr_gaus_var_slct_tab.tex

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.91 & 0.59 & 0.97 & 0.97 & 0.90 & 0.56 & 0.74 \\ 
   50 & Precision & 0.39 & 0.43 & 0.74 & 0.84 & 0.89 & 0.39 & 0.25 \\ 
  100 & Precision &  & 0.34 & 0.53 & 0.72 & 0.91 & 0.29 & 0.25 \\ 
  200 & Precision &  & 0.27 & 0.42 & 0.52 & 0.92 & 0.33 & 0.25 \\ 
    4 & Recall & 1.00 & 1.00 & 0.87 & 0.84 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 1.00 & 0.98 & 0.96 & 1.00 & 1.00 & 0.75 \\ 
   50 & Recall & 1.00 & 1.00 & 0.85 & 0.99 & 1.00 & 1.00 & 0.25 \\ 
  100 & Recall &  & 1.00 & 0.84 & 0.97 & 1.00 & 1.00 & 0.25 \\ 
  200 & Recall &  & 1.00 & 0.78 & 0.88 & 1.00 & 0.98 & 0.25 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.91 & 0.59 & 0.96 & 0.94 & 0.91 & 0.54 & 0.58 \\ 
   50 & MCC & 0.57 & 0.59 & 0.76 & 0.90 & 0.92 & 0.57 & 0.18 \\ 
  100 & MCC &  & 0.54 & 0.61 & 0.81 & 0.94 & 0.48 & 0.22 \\ 
  200 & MCC &  & 0.49 & 0.52 & 0.64 & 0.95 & 0.52 & 0.23 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{ccccccccc}
  \hline
P & Metric & mgcv & LASSO & COSSO & Adaptive COSSO & BHAM & SB-GAM & spikeSlabGAM \\ 
  \hline
  4 & Precision & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ 
   10 & Precision & 0.91 & 0.59 & 0.97 & 0.97 & 0.90 & 0.56 & 0.99 \\ 
   50 & Precision & 0.39 & 0.43 & 0.74 & 0.84 & 0.89 & 0.39 & 0.99 \\ 
  100 & Precision &  & 0.34 & 0.53 & 0.72 & 0.91 & 0.29 & 0.99 \\ 
  200 & Precision &  & 0.27 & 0.42 & 0.52 & 0.92 & 0.33 & 0.99 \\ 
    4 & Recall & 1.00 & 1.00 & 0.87 & 0.84 & 1.00 & 1.00 & 1.00 \\ 
   10 & Recall & 1.00 & 1.00 & 0.98 & 0.96 & 1.00 & 1.00 & 1.00 \\ 
   50 & Recall & 1.00 & 1.00 & 0.85 & 0.99 & 1.00 & 1.00 & 1.00 \\ 
  100 & Recall &  & 1.00 & 0.84 & 0.97 & 1.00 & 1.00 & 1.00 \\ 
  200 & Recall &  & 1.00 & 0.78 & 0.88 & 1.00 & 0.98 & 1.00 \\ 
    4 & MCC &  &  &  &  &  &  &  \\ 
   10 & MCC & 0.91 & 0.59 & 0.96 & 0.94 & 0.91 & 0.54 & 0.99 \\ 
   50 & MCC & 0.57 & 0.59 & 0.76 & 0.90 & 0.92 & 0.57 & 1.00 \\ 
  100 & MCC &  & 0.54 & 0.61 & 0.81 & 0.94 & 0.48 & 1.00 \\ 
  200 & MCC &  & 0.49 & 0.52 & 0.64 & 0.95 & 0.52 & 0.99 \\ 
   \hline
\end{tabular}
\caption{} 
\label{}
\end{table}
